\documentclass{beamer}
\usepackage{beamerthemeshadow}
\usepackage{color}

\mode<presentation>
{
  \usetheme{Warsaw} %%% Change later
 \usecolortheme{dove}


  \setbeamercovered{transparent}
  % or whatever (possibly just delete it)
}
\setbeamertemplate{footline}[page number]{}


\begin{document}
\title{Adapting Clojure to an introductory CS classroom.}
\author{Elena Machkasova}
\institute[UMM] % (optional, but mostly needed)
{
 % \inst{1}%
  University of Minnesota, Morris
}
\date[]  
{Clojure/west, April 21 2015.}

\begin{frame}
  \titlepage
\end{frame}

\section{Why Clojure for intro CS?}

\begin{frame}
   \frametitle{ClojurEd project}
ClojurEd is a project at UMM: developing a beginner-friendly setup for Clojure. 


This is work in progress!!! 

{\large\bf  Lots}  still needs to be done before we can use Clojure in an introductory class. 
{\tt Need an icon here}
\end{frame}

\begin{frame}
   \frametitle{Where are we coming from?}
{\tt Need a map here; need to make bullet points appear one by one}

\begin{itemize}
\item UMM: a small undergraduate-only liberal arts college.
\item Morris: a rural town 3.5 hours from UMN-TC. 
\item Undergraduate research. 
\item Use Lisp in an introductory CS class. 
\end{itemize}
\end{frame}

\begin{frame}
   \frametitle{A programming language for introductory class}
\begin{itemize}
\item {\bf Use} a programming language in an introductory class.
\item {\bf  Teach} concepts and skills.
\item {\bf  Teach} CS-style problem solving.
\item The language needs to be simple, well-defined, and non-distracting (Felleisen et al, 2004).
\item Dynamically typed.
\item Functional languages are useful: focus on functions, modularity, abstraction.
\item Functional languages: higher order functions (needed now with Javascript-based web dev)
\item Interactive development: REPL. 
%\item Lisps have simple syntax and clearly defined semantics.
\end{itemize}
\end{frame}

\begin{frame}
   \frametitle{Current use of Lisp/Clojure in classes}
\begin{itemize}
\item UMM uses Racket (a Lisp) in an introductory class. 
\item 2010: a UMM student mentioned Clojure. 
\item We've used Clojure in upper-level courses (Programming Languages, Programming for Parallel Architecture).
\item Would like to use it in an introductory class (it's a long way).
\item A couple of other schools use Clojure: Hampshire College, MA. 
\end{itemize}
\end{frame}

\begin{frame}
   \frametitle{What Clojure brings to the table?}
Students are curious, would like to expand and apply what they learn. 

Clojure offers:
\begin{itemize}
\item A large community that students can explore/benefit from: libraries, community-maintained docs, textbooks, blog posts, open source projects, meetups,....
\item Concurrency.
\item Integration with Java. 
\end{itemize}
\end{frame}

\section{Why {\bf not} (yet) Clojure}

\begin{frame}
   \frametitle{What's lacking}
\begin{itemize}
\item Usability of error messages. {\tt give an example}
\item Beginner-friendly IDE. 
\item Beginner-friendly project manager. 
%\item Can't expect new students use emacs/vim and command line (at least if we want to keep CS enrollments/diversity). 
\item Beginner-friendly graphical libraries. 
\item Beginner-friendly textbooks (focus on concepts, use language as a learning tool). 
\end{itemize}
\end{frame}

\section{Error messages transformations}

\begin{frame}
   \frametitle{(Non)Usability of error messages}
\begin{itemize}
\item 
\end{itemize}
\end{frame}


\subsection{Regular expressions}

\subsection{Pre-conditions}

\subsection{Idea: hints and scenarios}

\section{Beginner-friendly tools}

\section{Future work (lots of it!), acknowledgments}

\begin{frame}
   \frametitle{Many thanks to:}
\begin{itemize}
\item 
\item 
\item MN Clojure group and Boston Clojure meetup. 
\end{itemize}
\end{frame}

\begin{frame}
   \frametitle{Our resources}
\begin{itemize}
\item 
\end{itemize}
\end{frame}

\end{document}
